---
title: "DSC530 Term Project"
author: "A. Kendell Davis"
date: "2/29/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Preliminary Data preparation
All of the following code is designed in preparation to create the results supplied in my EDA

```{r Leisure.data}
library(tidyverse)
Leisure.data$Year <- as.factor(Leisure.data$Year)
leisure2010 <- Leisure.data[Leisure.data$Year == "2010", ]
leisure2011 <- Leisure.data[Leisure.data$Year == "2011", ]
leisure2012 <- Leisure.data[Leisure.data$Year == "2012", ]
leisure2013 <- Leisure.data[Leisure.data$Year == "2013", ]
leisure2014 <- Leisure.data[Leisure.data$Year == "2014", ]
leisure2015 <- Leisure.data[Leisure.data$Year == "2015", ]
leisure2016 <- Leisure.data[Leisure.data$Year == "2016", ]
leisure2017 <- Leisure.data[Leisure.data$Year == "2017", ]
leisure2018 <- Leisure.data[Leisure.data$Year == "2018", ]
leisure_once_year <- Leisure.data[Leisure.data$Frequency == "Participated in the last 12 months", ]
leisure_multi_week <- Leisure.data[Leisure.data$Frequency == "Weekly Participation (multiple)", ]
leisure_once_week <- Leisure.data[Leisure.data$Frequency == "Weekly Participation (once)", ]
leisure_multi_month <- Leisure.data[Leisure.data$Frequency == "Monthly Participation (multiple)", ]
leisure_once_month <- Leisure.data[Leisure.data$Frequency == "Monthly Participation (once)", ]
leisure_activity <- distinct(Leisure.data, Activity, .keep_all = TRUE)
FrequencyLevel <- c("Participated in the last 12 months","Weekly Participation (multiple)", "Weekly Participation (once)", "Monthly Participation (multiple)", "Monthly Participation (once)")
```
## Histogram Plots
All of the following code is designed to create the histogram plots required for my EDA

```{r}
ggplot(data = leisure2010, aes(x = Frequency, y = Percentage)) + geom_col(aes(fill = Activity), position = "dodge") + scale_x_discrete(limits = FrequencyLevel) + labs(title = "Leisure Activities for 2010") + guides(fill = "none") + geom_vline(xintercept = 1.5)
ggplot(data = leisure2011, aes(x = Frequency, y = Percentage)) + geom_col(aes(fill = Activity), position = "dodge") + scale_x_discrete(limits = FrequencyLevel) + labs(title = "Leisure Activities for 2011") + guides(fill = "none") + geom_vline(xintercept = 1.5)
ggplot(data = leisure2012, aes(x = Frequency, y = Percentage)) + geom_col(aes(fill = Activity), position = "dodge") + scale_x_discrete(limits = FrequencyLevel) + labs(title = "Leisure Activities for 2012") + guides(fill = "none") + geom_vline(xintercept = 1.5)
ggplot(data = leisure2013, aes(x = Frequency, y = Percentage)) + geom_col(aes(fill = Activity), position = "dodge") + scale_x_discrete(limits = FrequencyLevel) + labs(title = "Leisure Activities for 2013") + guides(fill = "none") + geom_vline(xintercept = 1.5)
ggplot(data = leisure2014, aes(x = Frequency, y = Percentage)) + geom_col(aes(fill = Activity), position = "dodge") + scale_x_discrete(limits = FrequencyLevel) + labs(title = "Leisure Activities for 2014") + guides(fill = "none") + geom_vline(xintercept = 1.5)
ggplot(data = leisure2015, aes(x = Frequency, y = Percentage)) + geom_col(aes(fill = Activity), position = "dodge") + scale_x_discrete(limits = FrequencyLevel) + labs(title = "Leisure Activities for 2015") + guides(fill = "none") + geom_vline(xintercept = 1.5)
ggplot(data = leisure2016, aes(x = Frequency, y = Percentage)) + geom_col(aes(fill = Activity), position = "dodge") + scale_x_discrete(limits = FrequencyLevel) + labs(title = "Leisure Activities for 2016") + guides(fill = "none") + geom_vline(xintercept = 1.5)
ggplot(data = leisure2017, aes(x = Frequency, y = Percentage)) + geom_col(aes(fill = Activity), position = "dodge") + scale_x_discrete(limits = FrequencyLevel) + labs(title = "Leisure Activities for 2017") + guides(fill = "none") + geom_vline(xintercept = 1.5)
ggplot(data = leisure2018, aes(x = Frequency, y = Percentage)) + geom_col(aes(fill = Activity), position = "dodge") + scale_x_discrete(limits = FrequencyLevel) + labs(title = "Leisure Activities for 2018") + guides(fill = "none") + geom_vline(xintercept = 1.5)
ggplot(data = leisure_activity, aes(x = Locality)) + geom_histogram(stat = "count")
ggplot(data = leisure_once_year, aes(x = Percentage)) + geom_histogram(binwidth = 1) + labs(title = "Leisure Activities Participated in the Last 12 Months")
ggplot(data = leisure_multi_week, aes(x = Percentage)) + geom_histogram(binwidth = 1) + labs(title = "Leisure Activities Participated in 2+ Times per Week")
ggplot(data = leisure_once_week, aes(x = Percentage)) + geom_histogram(binwidth = 1) + labs(title = "Leisure Activities Participated in 1 Time per Week")
ggplot(data = leisure_multi_month, aes(x = Percentage)) + geom_histogram(binwidth = 1) + labs(title = "Leisure Activities Participated in 2-3 Times per Month")
ggplot(data = leisure_once_month, aes(x = Percentage)) + geom_histogram(binwidth = 1) + labs(title = "Leisure Activities Participated in 1 Time per Month")
```
## Analytical Plots
All of the following code is designed to create the plots designed for visual analytics required for my EDA (PMF, CDF, analytical distribution, etc.)

```{r}
ggplot(data = Leisure.data, aes(x = Frequency)) + geom_bar(aes(fill = Locality, weight = Percentage), position = "dodge") + scale_x_discrete(limits = FrequencyLevel, labels = function(x) str_wrap(x, width = 10)) + facet_wrap(~ Year)
ggplot(data = leisure_once_year, aes(x = Percentage)) + stat_ecdf(geom = "step")
ggplot(data = Leisure.data, aes(x = Frequency, y = Percentage)) + geom_point(aes(color = Locality), position = "jitter") + scale_x_discrete(limits = FrequencyLevel, labels = function(x) str_wrap(x, width = 10)) + facet_wrap(~ Year)
```
## Statistical Analysis
All of the following code applies the statistical analyses required for my EDA

```{r}
leisure_local <- leisure_once_year[leisure_once_year$Locality == "Local", ]
leisure_remote <- leisure_once_year[leisure_once_year$Locality == "Remote", ]
t.test(leisure_local$Percentage, leisure_remote$Percentage)
leisure_corr <- lm(Percentage ~ Activity + Year, leisure_once_year)
summary(leisure_corr)
```





